Growing Up with Nell: A Narrative Interface for Literacy

### 2012-03-12 paper.tex
Photoshop Nell into the XO-3 photo.
Tweak conclusion.

\section{A Lesson from Nell} \label{sec:lesson}
\begin{figure}
\centering
\epsfig{file=xo3-3.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}
% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl named Rahel turns on her
new tablet computer. The solar-powered machine speaks to her:
\textit{``Hello!  Would you like to hear a story?''}

@@

\section{Conclusions}
We have described the design of a novel narrative direct-interface
system for teaching literacy, which is personalized for and grows with
its child owner.  Personalized direct interface engages the child, and
narrative guides them through Nell's pedagogic material.  The low-cost
solar-powered hardware allows Nell to reach further into the
least-developed areas of the world, to help those far from traditional
educational infrastructure.

We are in the process of implementing the Nell system, and expect to
do initial deployments in Africa later this year.

>>>>

\section{A Lesson from Nell} \label{sec:lesson}
\begin{figure}
\centering
\epsfig{file=xo3-4.eps, width=3.2in}
\caption{Nell's solar-powered hardware platform.  The tablet design
  allows for direct interaction.}\label{fig:xo3}
\end{figure}
% tell a nell story up front
Miles from the nearest school, a young Ethiopian girl named Rahel turns on her
new tablet computer. The solar-powered machine speaks to her:
\textit{``Hello!  Would you like to hear a story?''}

@@

\section{Conclusions}
We have described the design of a novel narrative direct-interface
system for teaching literacy, which is personalized for and grows with
its child owner.  Personalized direct interface engages the child, and
narrative guides them through the pedagogic material.  The low-cost
solar-powered hardware allows Nell to reach further into the
least-developed areas of the world, to help those far from traditional
educational infrastructure.

We are in the process of implementing the Nell system, and expect to
field initial deployments of subsets of Nell in Africa later this year.
